---
title: "Land Ownership"
output: html_document
date: "2022-10-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_lbs, echo = FALSE, message = FALSE, warnings = FALSE}
library(tidyverse)
library(here)
library(leaflet)
library(scico)
library(scales)
library(sf)
library(ggmap)
library(ggspatial)
library(rnaturalearthdata)
library(rnaturalearth)
library(ggsn)
```

# Read in watershed extents
```{r}
watershed_ext <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/Saline_lake_watershed_extents/lake_watersheds.shp')) 
watershed_ext_5070 <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/Saline_lake_watershed_extents/lake_watersheds_5070.shp')) 
watershed_ext_huc10 <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/Saline_lake_watershed_extents/lake_watersheds_by_huc10.shp'))
watershed_ext_huc10_5070 <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/Saline_lake_watershed_extents/lake_watersheds_by_huc10_5070.shp')) 
```

# Read in lake shapefiles
```{r}
saline_lakes <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/saline_lakes/saline_lakes.shp')) 
saline_lakes_5070 <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/saline_lakes/saline_lakes_5070.shp')) 
```

# Read in Great Basin Dessert Band
```{r}
gbd_bnd <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/GreatBasinDessertBnd_220721/GreatBasinDessertBnd.shp')) %>% 
  st_transform(crs=st_crs(saline_lakes_5070))
```

# Read in PAD/land ownership data
```{r}
pad <- st_read(here('1_fetch/in/Shapefiles_220721/PADUS_3_0VA.shp')) %>% 
  st_transform(crs=st_crs(saline_lakes_5070)) %>% 
  select(OBJECTI, Mng_Typ, Mang_Nm, Unit_Nm, GIS_Acr, MngTp_D, MngNm_D, BndryNm, ST_Name)
```
# Read in states layer
```{r}
states <- st_read(here('1_fetch/in/states_shp/statesp010g.shp')) %>% 
  st_transform(crs=st_crs(saline_lakes_5070))
```

# Intersect `pad` to each of `gbd_bnd, `saline_lakes_5070`, and `watershed_ext_5070`/ `watershed_ext_huc10_5070`
```{r}
gbd_pad_int <- st_intersection(pad, gbd_bnd) 
saline_lakes_5070_pad_int <- st_intersection(pad, saline_lakes_5070)
watershed_ext_huc10_5070_pad_int <- st_intersection(pad, watershed_ext_huc10_5070)
watershed_ext_5070_pad_int <- st_intersection(pad, watershed_ext_5070)

```

# add in an area count column to the dfs
```{r}
gbd_pad_int$area <- st_area(gbd_pad_int$geometry)
saline_lakes_5070_pad_int$area <- st_area(saline_lakes_5070_pad_int$geometry)
watershed_ext_huc10_5070_pad_int$area <- st_area(watershed_ext_huc10_5070_pad_int$geometry)
watershed_ext_5070_pad_int$area <- st_area(watershed_ext_5070_pad_int$geometry)

# plot the layers to visually check result of intersect
plot(gbd_pad_int$geometry, col='green')
plot(pad$geometry)
plot(gbd_pad_int$geometry, col='red')

```

# group data by Mng_Typ and calculate the total land area per Mng_Typ
```{r}
gbdByMng <- gbd_pad_int %>%
  group_by(Mng_Typ) %>%
  summarise(areaMng_Typ = sum(area))

# change data type of areaMng_Typ field to numeric (from 'S3: units' with m^2 suffix)
gbdByMng$areaMng_Typ <- as.numeric(gbdByMng$areaMng_Typ)

salineLakes5070ByMng <- saline_lakes_5070_pad_int %>%
  group_by(Mng_Typ, GNIS_Nm) %>%
  summarise(areaMng_Typ = sum(area))

salineLakes5070ByMng$areaMng_Typ <- as.numeric(salineLakes5070ByMng$areaMng_Typ)

watershedExtHuc10_5070ByMng <- watershed_ext_huc10_5070_pad_int %>%
  group_by(Mng_Typ, HUC10_N) %>%
  summarise(areaMng_Typ = sum(area))

watershedExtHuc10_5070ByMng$areaMng_Typ <- as.numeric(watershedExtHuc10_5070ByMng$areaMng_Typ)

watershedExt5070ByMng <- watershed_ext_5070_pad_int %>%
  group_by(Mng_Typ, lk_w_st) %>%
  summarise(areaMng_Typ = sum(area))

watershedExt5070ByMng$areaMng_Typ <- as.numeric(watershedExt5070ByMng$areaMng_Typ)
```

# group data by MngNm_D and calculate the total land area per MngNm_D (more detailed Manamgement Types)
```{r}
gbdByMngNm <- gbd_pad_int %>%
  group_by(MngNm_D) %>%
  summarise(areaMngNm_Typ = sum(area))

# change data type of areaMng_Typ field to numeric (from 'S3: units' with m^2 suffix)
gbdByMngNm$areaMngNm_Typ <- as.numeric(gbdByMngNm$areaMngNm_Typ)

salineLakes5070ByMngNm <- saline_lakes_5070_pad_int %>%
  group_by(MngNm_D, GNIS_Nm) %>%
  summarise(areaMngNm_Typ = sum(area))

salineLakes5070ByMngNm$areaMngNm_Typ <- as.numeric(salineLakes5070ByMngNm$areaMngNm_Typ)

watershedExtHuc10_5070ByMngNm <- watershed_ext_huc10_5070_pad_int %>%
  group_by(MngNm_D, HUC10_N) %>%
  summarise(areaMngNm_Typ = sum(area))

watershedExtHuc10_5070ByMngNm$areaMngNm_Typ <- as.numeric(watershedExtHuc10_5070ByMngNm$areaMngNm_Typ)

watershedExt5070ByMngNm <- watershed_ext_5070_pad_int %>%
  group_by(MngNm_D, lk_w_st) %>%
  summarise(areaMngNm_Typ = sum(area))

watershedExt5070ByMngNm$areaMngNm_Typ <- as.numeric(watershedExt5070ByMngNm$areaMngNm_Typ)
```


# Plot 
```{r}
ggplot(data = gbdByMngNm%>% st_transform(crs=st_crs(saline_lakes))) +
  geom_sf(aes(fill = MngNm_D))

ggplot(data = salineLakes5070ByMng) +
  geom_sf(aes(fill = Mng_Typ))

ggplot(data = watershedExtHuc10_5070ByMngNm_grp) +
  geom_sf(aes(fill = MngGroup))

ggplot(data = watershedExt5070ByMng) +
  geom_sf(aes(fill = Mng_Typ))
  
```

# Group some of the Management Type names to reduce colors needed 
```{r}
gbdByMngNm_grp <- gbdByMngNm %>% 
  mutate(MngGroup = case_when(
   MngNm_D == "American Indian Lands" ~ "Native American areas", 
   MngNm_D == "Agricultural Research Service" ~ "Federal - other",
    MngNm_D == "Army Corps of Engineers" ~ "Federal - other", 
    MngNm_D == "Department of Energy" ~ "Federal - other",
    MngNm_D == "Natural Resources Conservation Service" ~ "Federal - other", 
    MngNm_D == "State Department of Conservation" ~ "State entities",
    MngNm_D == "Other or Unknown State Land" ~ "State entities", 
    MngNm_D == "State Park and Recreation" ~ "State entities",
    MngNm_D == "State Department of Land" ~ "State entities",
    MngNm_D == "State Fish and Wildlife" ~ "State entities", 
    MngNm_D == "State Department of Natural Resources" ~ "State entities", 
    MngNm_D == "State Land Board" ~ "State entities", 
    MngNm_D == "Regional Agency Land" ~ "Regional entites",
    MngNm_D == "County Land" ~ "Municipal entities",
    MngNm_D == "City Land" ~ "Municipal entities", 
    MngNm_D == "Non-Governmental Organization" ~ "NGO",
    TRUE ~ MngNm_D
  ))

salineLakesByMngNm_grp <- salineLakes5070ByMngNm %>% 
  mutate(MngGroup = case_when(
   MngNm_D == "American Indian Lands" ~ "Native American areas", 
   MngNm_D == "Agricultural Research Service" ~ "Federal - other",
    MngNm_D == "Army Corps of Engineers" ~ "Federal - other", 
    MngNm_D == "Department of Energy" ~ "Federal - other",
    MngNm_D == "Natural Resources Conservation Service" ~ "Federal - other", 
    MngNm_D == "State Department of Conservation" ~ "State entities",
    MngNm_D == "Other or Unknown State Land" ~ "State entities", 
    MngNm_D == "State Park and Recreation" ~ "State entities",
    MngNm_D == "State Department of Land" ~ "State entities",
    MngNm_D == "State Fish and Wildlife" ~ "State entities", 
    MngNm_D == "State Department of Natural Resources" ~ "State entities", 
    MngNm_D == "State Land Board" ~ "State entities", 
    MngNm_D == "Regional Agency Land" ~ "Regional entites",
    MngNm_D == "County Land" ~ "Municipal entities",
    MngNm_D == "City Land" ~ "Municipal entities", 
    MngNm_D == "Non-Governmental Organization" ~ "NGO",
    TRUE ~ MngNm_D
  ))

watershedExtHuc10_5070ByMngNm_grp <- watershedExtHuc10_5070ByMngNm %>% 
  mutate(MngGroup = case_when(
   MngNm_D == "American Indian Lands" ~ "Native American areas", 
   MngNm_D == "Agricultural Research Service" ~ "Federal - other",
    MngNm_D == "Army Corps of Engineers" ~ "Federal - other", 
    MngNm_D == "Department of Energy" ~ "Federal - other",
    MngNm_D == "Natural Resources Conservation Service" ~ "Federal - other", 
    MngNm_D == "State Department of Conservation" ~ "State entities",
    MngNm_D == "Other or Unknown State Land" ~ "State entities", 
    MngNm_D == "State Park and Recreation" ~ "State entities",
    MngNm_D == "State Department of Land" ~ "State entities",
    MngNm_D == "State Fish and Wildlife" ~ "State entities", 
    MngNm_D == "State Department of Natural Resources" ~ "State entities", 
    MngNm_D == "State Land Board" ~ "State entities", 
    MngNm_D == "Regional Agency Land" ~ "Regional entites",
    MngNm_D == "County Land" ~ "Municipal entities",
    MngNm_D == "City Land" ~ "Municipal entities", 
    MngNm_D == "Non-Governmental Organization" ~ "NGO",
    TRUE ~ MngNm_D
  ))
```

```{r}
mapBound <- gbdByMngNm_grp %>% st_transform(crs=st_crs(4326)) %>% 
  st_bbox() %>% st_as_sfc() %>% st_buffer(0.25) %>%
  st_bbox() %>% as.numeric()

man_basemap <- ggmap::get_stamenmap(bbox = mapBound, zoom = 6, messaging = FALSE, maptype = 'terrain-lines')

manualcolors<-c('black','forestgreen', 'red2', 'orange', 'cornflowerblue', 'darkolivegreen4', 'indianred1', 'tan4', 'darkblue','firebrick4',  'yellowgreen', 'lightsalmon', 'tan3','darkgray', 'wheat4', 'moccasin', 'mediumvioletred','cadetblue1',
                "darkolivegreen1" , "tomato3" , "#7CE3D8","gainsboro")

greatBasin <- ggmap(man_basemap) +
  # geom_sf(data = states %>% st_transform(4326),
  #              aes(group = STATE_ABBR),
  #         alpha = 0.8,
  #         fill = NA,
  #         color = "grey60", inherit.aes = FALSE)+
  geom_sf(data = gbdByMngNm_grp %>% st_transform(4326), aes(fill = MngGroup, color = MngGroup), inherit.aes = FALSE) +
  coord_sf(crs = st_crs(4326)) +
scale_color_manual(values = manualcolors) +
  scale_fill_manual(values = manualcolors) + 
  labs(fill='Management Type') +
  guides(color="none", 
         fill = guide_legend(override.aes=list(linetype = 0))) + 
  theme_void() +
  theme(legend.position="bottom",
        legend.title=element_blank()) +
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.2, "in"), pad_y = unit(0.15, "in"),
                         height = unit(0.5, "in"), width= unit(0.2, "in"),
                         style = north_arrow_orienteering(fill = c("black", "black"),
                                                          line_col = "black",
                                                          text_col = "black"))


ggsave(here("6_visualize/out/greatBasin.png"), width = 10, height = 7, dpi = 500)
```

```{r}
mapBound <- salineLakesByMngNm_grp %>% st_transform(crs=st_crs(4326)) %>% 
  st_bbox() %>% st_as_sfc() %>% st_buffer(0.25) %>%
  st_bbox() %>% as.numeric()

man_basemap <- ggmap::get_stamenmap(bbox = mapBound, zoom = 7, messaging = FALSE, maptype = 'terrain-lines')

salineLakes <- ggmap(man_basemap) +
  # geom_sf(data = states %>% st_transform(4326),
  #              aes(group = STATE_ABBR),
  #         alpha = 0.3,
  #         fill = NA,
  #         color = "grey60", inherit.aes = FALSE,
  #         linetype = "11", size = 0.8) +
  geom_sf(data = salineLakesByMngNm_grp %>% st_transform(4326), aes(fill = MngGroup, color=MngGroup),
          inherit.aes = FALSE) + 
  coord_sf(crs = st_crs(4326)) + 
scale_color_manual(values = manualcolors) +
  scale_fill_manual(values = manualcolors) + 
 labs(fill='Management Type') +
  guides(color="none", 
         fill = guide_legend(override.aes=list(linetype = 0))) +
  theme_void() +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.key = element_blank()) +
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.2, "in"), pad_y = unit(0.15, "in"),
                         height = unit(0.5, "in"), width= unit(0.2, "in"),
                         style = north_arrow_orienteering(fill = c("black", "black"),
                                                          line_col = "black",
                                                          text_col = "black"))

ggsave(here("6_visualize/out/salineLakes.png"), width = 10, height = 7, dpi = 500)

```

```{r}
mapBound <- watershedExtHuc10_5070ByMngNm_grp %>% st_transform(crs=st_crs(4326)) %>% 
  st_bbox() %>% st_as_sfc() %>% st_buffer(0.25) %>%
  st_bbox() %>% as.numeric()

man_basemap <- ggmap::get_stamenmap(bbox = mapBound, zoom = 5, messaging = FALSE, maptype = 'terrain-lines')

salineLakes <- ggmap(man_basemap) +
  # geom_sf(data = states %>% st_transform(4326),
  #              aes(group = STATE_ABBR),
  #         alpha = 0.3,
  #         fill = NA,
  #         color = "grey60", inherit.aes = FALSE,
  #         linetype = "11", size = 0.8) +
  geom_sf(data = watershedExtHuc10_5070ByMngNm_grp %>% st_transform(4326), aes(fill = MngGroup, color=MngGroup),
          inherit.aes = FALSE) + 
  coord_sf(crs = st_crs(4326)) + 
scale_color_manual(values = manualcolors) +
  scale_fill_manual(values = manualcolors) + 
 labs(fill='Management Type') +
  guides(color="none", 
         fill = guide_legend(override.aes=list(linetype = 0))) +
  theme_void() +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.key = element_blank()) +
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.2, "in"), pad_y = unit(0.15, "in"),
                         height = unit(0.5, "in"), width= unit(0.2, "in"),
                         style = north_arrow_orienteering(fill = c("black", "black"),
                                                          line_col = "black",
                                                          text_col = "black"))

ggsave(here("6_visualize/out/watershedExtentHuc10.png"), width = 10, height = 7, dpi = 500)
```


