---
title: "Saline Lakes Land Ownership Visualizations"
format: pptx
editor: visual
reference-doc: ../src/template.pptx
---

```{r,  warning=FALSE}
library(tidyverse)
library(here)
library(leaflet)
library(scico)
library(scales)
library(sf)
library(ggmap)
library(ggspatial)
library(rnaturalearthdata)
library(rnaturalearth)
library(ggsn)
library(rmapshaper)
library(maptiles)
library(tidyterra)
library(cowplot)

# Read in viz R script 
source('../../6_visualize/src/plot_land_data.R')

# Read in data to render
p2_gbd_ByMngNm_reduce <- readRDS("../../1_fetch/out/gbd_ByMngNm_reduce.rds")
p2_watershedExt_ByMngNm_reduce <- readRDS("../../1_fetch/out/watershedExt_ByMngNm_reduce.rds")
p2_gbd_pal <- readRDS("../../1_fetch/out/gbd_pal.rds")
p2_gbdByMngNm_grp_pArea <- readRDS("../../1_fetch/out/gbdByMngNm_grp_pArea.rds")
p2_watershedExtByMngNm_grp_pArea <- readRDS("../../1_fetch/out/watershedExtByMngNm_grp_pArea.rds")
p1_saline_lakes_sf <-  readRDS("../../1_fetch/out/saline_lakes_sf.rds")
p1_watershed_ext_sf <- readRDS("../../1_fetch/out/watershed_ext_sf.rds")
p1_gbd_bnd <- readRDS("../../1_fetch/out/gbd_bnd.rds")
```


# Great Basin

```{r,  warning=FALSE}
# Broader groupings 
greaBasin_map <- map_greatBasin(data = p2_gbd_ByMngNm_reduce, join = p2_gbd_pal, zoom = 7 )
greatBasin_chart <- chart_greatBasinLand(data = p2_gbdByMngNm_grp_pArea)
greatBasin_inset <- map_basin_inset(data_gbd = p1_gbd_bnd, data_lakes = p1_saline_lakes_sf,proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(greaBasin_map+ theme(legend.position = 'bottom'),
          greatBasin_chart,rel_widths = c(0.91, 0.93), align = "h")

gg_inset_map1 = ggdraw() +
  draw_plot(combine) +
  draw_plot(greatBasin_inset, x= -0.005, y = 0.127, width = 0.18, height = 0.175)

gg_inset_map1
```

# Great Basin - Federal Lands

```{r}
greatBasin_chartFed <- chart_basinFederal(data = p2_gbdByMngNm_grp_pArea)
greaBasin_mapFed <- map_greatBasinFederal(data = p2_gbd_ByMngNm_reduce, join = p2_gbd_pal, zoom = 7 )


combineFed <- plot_grid(greaBasin_mapFed+ theme(legend.position = 'none'),
          greatBasin_chartFed,rel_widths = c(0.91, 0.93), align = "h")

gg_inset_mapFed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(greatBasin_inset, x= -0.0015, y = 0.078, width = 0.18, height = 0.175)

gg_inset_mapFed

```

# Carson Lake, NV

```{r,  warning=FALSE}
lakeCarson_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Carson Lake,NV'))
lakeCarson_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Carson Lake,NV'))
lakeCarson_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Carson Lake,NV'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeCarson_map+ theme(legend.position = 'bottom'), lakeCarson_chart,rel_widths = c(1.18, 1.25))

gg_inset_map2 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeCarson_inset, x= 0.305, y = 0.12, width = 0.15, height = 0.15)

gg_inset_map2
```

# Carson Lake, NV - Federal Lands
```{r}
lakeCarson_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Carson Lake,NV'))
lakeCarson_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Carson Lake,NV'))

combineFed <- plot_grid(lakeCarson_mapFed+ theme(legend.position = 'none'), lakeCarson_chartFed,rel_widths = c(1.18, 1.25))

gg_inset_map2Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeCarson_inset, x= 0.310, y = 0.06, width = 0.15, height = 0.15)

gg_inset_map2Fed 
```


# Eagle Lake, CA 

```{r,  warning=FALSE}
lakeEagle_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Eagle Lake,CA'))
## issue here with watershed chart not showing the unknown percentage/bar plot?
lakeEagle_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Eagle Lake,CA'))
lakeEagle_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Eagle Lake,CA'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeEagle_map+ theme(legend.position = 'bottom'), lakeEagle_chart,rel_widths = c(1.20, 1.15))


gg_inset_map3 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeEagle_inset, x= 0.363, y = 0.220, width = 0.15, height = 0.15)

gg_inset_map3

```


# Eagle Lake, CA - Federal Lands
```{r}
lakeEagle_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Eagle Lake,CA'))
lakeEagle_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Eagle Lake,CA'))

combineFed <- plot_grid(lakeEagle_mapFed+ theme(legend.position = 'none'), lakeEagle_chartFed,rel_widths = c(1.18, 1.25))

gg_inset_map3Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeEagle_inset, x= 0.341, y = 0.195, width = 0.15, height = 0.15)

gg_inset_map3Fed 
```

# Franklin Lake, NV

```{r,  warning=FALSE}
lakeFranklin_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Franklin Lake,NV'))
lakeFranklin_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Franklin Lake,NV'))
lakeFranklin_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Franklin Lake,NV'), proj = st_crs(p1_gbd_bnd))


combine <- plot_grid(lakeFranklin_map+ theme(legend.position = 'bottom'), lakeFranklin_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map4 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeFranklin_inset, x= 0.102, y = 0.11, width = 0.15, height = 0.15)

gg_inset_map4

```

# Franklin Lake, NV - Federal Lands

```{r}
lakeFranklin_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Franklin Lake,NV'))
lakeFranklin_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Franklin Lake,NV'))

combineFed <- plot_grid(lakeFranklin_mapFed+ theme(legend.position = 'none'), lakeFranklin_chartFed,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map4Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeFranklin_inset,x= 0.095, y = 0.06, width = 0.15, height = 0.15)

gg_inset_map4Fed 
```


# Goose Lake, CA

```{r,  warning=FALSE}
lakeGoose_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Goose Lake,CA'))
lakeGoose_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Goose Lake,CA'))
lakeGoose_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Goose Lake,CA'), proj = st_crs(p1_gbd_bnd))

combine<- plot_grid(lakeGoose_map+ theme(legend.position = 'bottom'), lakeGoose_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map5 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeGoose_inset, x= 0.058, y = 0.115, width = 0.15, height = 0.15)

gg_inset_map5

```

# Goose Lake, CA - Federal Lands

```{r}
lakeGoose_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Goose Lake,CA'))
lakeGoose_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Goose Lake,CA'))

combineFed <- plot_grid(lakeGoose_mapFed+ theme(legend.position = 'none'), lakeGoose_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map5Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeGoose_inset, x= 0.044, y = 0.07, width = 0.15, height = 0.15)

gg_inset_map5Fed 
```

# Great Salt Lake, UT

```{r,  warning=FALSE}
lakeGreatSalt_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Great Salt Lake,UT'))
lakeGreatSalt_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Great Salt Lake,UT'))
lakeGreatSalt_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Great Salt Lake,UT'), proj = st_crs(p1_gbd_bnd))

combine<- plot_grid(lakeGreatSalt_map+ theme(legend.position = 'bottom'), lakeGreatSalt_chart,rel_widths = c(1.18, 1.25), rel_heights = c(0.55, 0.55))

gg_inset_map6 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeGreatSalt_inset, x= 0.035, y = 0.12, width = 0.15, height = 0.15)

gg_inset_map6
```

# Great Salt Lake, UT - Federal Lands

```{r}
lakeGreatSalt_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Great Salt Lake,UT'))
lakeGreatSalt_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Great Salt Lake,UT'))

combineFed <- plot_grid(lakeGreatSalt_mapFed+ theme(legend.position = 'none'), lakeGreatSalt_chartFed,rel_widths = c(1.18, 1.25), rel_heights = c(0.55, 0.55))

gg_inset_map6Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeGreatSalt_inset,x= 0.028, y = 0.06, width = 0.15, height = 0.15)

gg_inset_map6Fed 
```


# Harney Lake, OR

```{r,  warning=FALSE}
lakeHarney_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Harney Lake,OR'))
lakeHarney_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Harney Lake,OR'))
lakeHarney_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Harney Lake,OR'), proj = st_crs(p1_gbd_bnd))


combine<- plot_grid(lakeHarney_map+ theme(legend.position = 'bottom'), lakeHarney_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map7 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeHarney_inset, x= 0.075, y = 0.102, width = 0.15, height = 0.15)

gg_inset_map7
```

#  Harney Lake, OR - Federal Lands

```{r}
lakHarney_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Harney Lake,OR'))
lakeHarney_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Harney Lake,OR'))

combineFed <- plot_grid(lakHarney_mapFed+ theme(legend.position = 'none'), lakeHarney_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map7Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeHarney_inset,  x= 0.058, y = 0.073, width = 0.15, height = 0.15)

gg_inset_map7Fed 
```

# Honey Lake, CA

```{r,  warning=FALSE}
lakeHoney_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Honey Lake,CA'))
lakeHoney_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Honey Lake,CA'))
lakeHoney_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Honey Lake,CA'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeHoney_map+ theme(legend.position = 'bottom'), lakeHoney_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map8 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeHoney_inset, x= 0.02, y = 0.125, width = 0.15, height = 0.15)

gg_inset_map8
```

#  Honey Lake, CA - Federal Lands

```{r}
lakeHoney_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Honey Lake,CA'))
lakeHoney_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Honey Lake,CA'))

combineFed <- plot_grid(lakeHoney_mapFed+ theme(legend.position = 'none'), lakeHoney_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map8Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeHoney_inset, x= 0.0015, y = 0.075, width = 0.15, height = 0.15)

gg_inset_map8Fed 
```

# Lake Abert, OR

```{r,  warning=FALSE}
lakeAbert_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Lake Abert,OR'))
lakeAbert_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Lake Abert,OR'))
lakeAbert_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Lake Abert,OR'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeAbert_map+ theme(legend.position = 'bottom'), lakeAbert_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map9 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeAbert_inset, x= 0.038, y = 0.119, width = 0.15, height = 0.15)

gg_inset_map9
```

#  Lake Abert, OR - Federal Lands

```{r}
lakeAbert_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Lake Abert,OR'))
lakeAbert_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Lake Abert,OR'))

combineFed <- plot_grid(lakeAbert_mapFed+ theme(legend.position = 'none'), lakeAbert_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map9Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeAbert_inset, x= 0.020, y = 0.070, width = 0.15, height = 0.15)

gg_inset_map9Fed 
```

# Malheur Lake, OR

```{r,  warning=FALSE}
lakeMalheur_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Malheur Lake,OR'))
lakeMalheur_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Malheur Lake,OR'))
lakeMalheur_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Malheur Lake,OR'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeMalheur_map+ theme(legend.position = 'bottom'), lakeMalheur_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map10 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeMalheur_inset, x= 0.10, y = 0.108, width = 0.15, height = 0.15)

gg_inset_map10
```


# Malheur Lake, OR - Federal Lands
```{r}
lakeMalheur_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Malheur Lake,OR'))
lakeMalheur_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Malheur Lake,OR'))

combineFed <- plot_grid(lakeMalheur_mapFed+ theme(legend.position = 'none'), lakeMalheur_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map10Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeMalheur_inset, x= 0.085, y = 0.065, width = 0.15, height = 0.15)

gg_inset_map10Fed 
```

# Mono Lake, CA

```{r,  warning=FALSE}
lakeMono_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Mono Lake,CA'))
lakeMono_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Mono Lake,CA'))
lakeMono_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Mono Lake,CA'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeMono_map + theme(legend.position = 'bottom'), lakeMono_chart, rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map11 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeMono_inset, x= 0.325, y = 0.115, width = 0.15, height = 0.15)

gg_inset_map11
```

# Mono Lake, CA - Federal Lands

```{r}
lakeMono_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Mono Lake,CA'))
lakeMono_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Mono Lake,CA'))

combineFed <- plot_grid(lakeMono_mapFed+ theme(legend.position = 'none'), lakeMono_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map11Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeMono_inset, x= 0.321, y = 0.055, width = 0.15, height = 0.15)

gg_inset_map11Fed 
```

# Owens Lake, CA

```{r,  warning=FALSE}
lakeOwens_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Owens Lake,CA'))
lakeOwens_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Owens Lake,CA'))
lakeOwens_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Owens Lake,CA'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeOwens_map + theme(legend.position = 'bottom'), lakeOwens_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map12 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeOwens_inset, x= 0.075, y = 0.105, width = 0.15, height = 0.15)

gg_inset_map12
```

#  Owens Lake, CA - Federal Lands

```{r}
lakeOwens_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Owens Lake,CA'))
lakeOwens_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Owens Lake,CA'))

combineFed <- plot_grid(lakeOwens_mapFed+ theme(legend.position = 'none'), lakeOwens_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map12Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeOwens_inset, x= 0.060, y = 0.071, width = 0.15, height = 0.15)

gg_inset_map12Fed 
```

# Pyramid Lake, NV

```{r,  warning=FALSE}
lakePyramid_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Pyramid Lake,NV'))
lakePyramid_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Pyramid Lake,NV'))
lakePyramid_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Pyramid Lake,NV'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakePyramid_map + theme(legend.position = 'bottom'), lakePyramid_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map13 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakePyramid_inset, x= 0.272, y = 0.099, width = 0.15, height = 0.15)

gg_inset_map13
```

#  Pyramid Lake, NV- Federal Lands

```{r}
lakePyramid_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Pyramid Lake,NV'))
lakePyramid_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Pyramid Lake,NV'))

combineFed <- plot_grid(lakePyramid_mapFed+ theme(legend.position = 'none'), lakePyramid_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map13Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakePyramid_inset,  x= 0.268, y = 0.055, width = 0.15, height = 0.15)

gg_inset_map13Fed 
```

# Ruby Lake, NV

```{r,  warning=FALSE}
lakeRuby_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Ruby Lake,NV'))
lakeRuby_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Ruby Lake,NV'))
lakeRuby_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Ruby Lake,NV'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeRuby_map + theme(legend.position = 'bottom'), lakeRuby_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))
gg_inset_map14 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeRuby_inset, x= 0.270, y = 0.102, width = 0.15, height = 0.15)

gg_inset_map14
```

# Ruby Lake, NV - Federal Lands

```{r}
lakeRuby_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Ruby Lake,NV'))
lakeRuby_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Ruby Lake,NV'))

combineFed <- plot_grid(lakeRuby_mapFed+ theme(legend.position = 'none'), lakeRuby_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))
gg_inset_map14Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeRuby_inset,  x= 0.268, y = 0.054, width = 0.15, height = 0.15)

gg_inset_map14Fed 
```

# Sevier Lake, UT

```{r,  warning=FALSE}
lakeSevier_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Sevier Lake,UT'))
lakeSevier_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Sevier Lake,UT'))
lakeSevier_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Sevier Lake,UT'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeSevier_map + theme(legend.position = 'bottom'), lakeSevier_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map15 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeSevier_inset, x= 0.062, y = 0.110, width = 0.15, height = 0.15)

gg_inset_map15
```

# Sevier Lake, UT - Federal Lands
```{r}
lakeSevier_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Sevier Lake,UT'))
lakeSevier_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Sevier Lake,UT'))

combineFed <- plot_grid(lakeSevier_mapFed+ theme(legend.position = 'none'), lakeSevier_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map15Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeSevier_inset, x= 0.048, y = 0.048, width = 0.15, height = 0.15)

gg_inset_map15Fed 
```

# Silver Lake, OR

```{r,  warning=FALSE}
lakeSilver_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Silver Lake,OR'))
lakeSilver_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Silver Lake,OR'))
lakeSilver_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Silver Lake,OR'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeSilver_map + theme(legend.position = 'bottom'), lakeSilver_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map16 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeSilver_inset, x= 0.0001, y = 0.122, width = 0.15, height = 0.15)

gg_inset_map16
```


# Silver Lake, OR - Federal Lands

```{r}
lakeSilver_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Silver Lake,OR'))
lakeSilver_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Silver Lake,OR'))

combineFed <- plot_grid(lakeSilver_mapFed+ theme(legend.position = 'none'), lakeSilver_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map16Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeSilver_inset, x= 0.0001, y = 0.108, width = 0.15, height = 0.15)

gg_inset_map16Fed 
```

# Summer Lake, OR

```{r,  warning=FALSE}
lakeSummer_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Summer Lake,OR'))
lakeSummer_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Summer Lake,OR'))
lakeSummer_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Summer Lake,OR'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeSummer_map + theme(legend.position = 'bottom'), lakeSummer_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map17 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeSummer_inset, x= 0.278, y = 0.093, width = 0.15, height = 0.15)

gg_inset_map17

```

# Summer Lake, OR - Federal Lands

```{r}
lakeSummer_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Summer Lake,OR'))
lakeSummer_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Summer Lake,OR'))

combineFed <- plot_grid(lakeSummer_mapFed+ theme(legend.position = 'none'), lakeSummer_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map17Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeSummer_inset, x= 0.275, y = 0.049, width = 0.15, height = 0.15)

gg_inset_map17Fed 
```

# Walker Lake, NV

```{r,  warning=FALSE}
lakeWalker_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Walker Lake,NV'))
lakeWalker_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Walker Lake,NV'))
lakeWalker_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Walker Lake,NV'), proj = st_crs(p1_gbd_bnd))

combine<- plot_grid(lakeWalker_map + theme(legend.position = 'bottom'), lakeWalker_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map18 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeWalker_inset, x= 0.329, y = 0.109, width = 0.15, height = 0.15)

gg_inset_map18
```


# Walker Lake, NV- Federal Lands

```{r}
lakeWalker_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Walker Lake,NV'))
lakeWalker_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Walker Lake,NV'))

combineFed <- plot_grid(lakeWalker_mapFed+ theme(legend.position = 'none'), lakeWalker_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))
gg_inset_map18Fed = ggdraw() +
  draw_plot(combineFed) + 
  draw_plot(lakeWalker_inset, x= 0.328, y = 0.058, width = 0.15, height = 0.15)
 
gg_inset_map18Fed 
```

# Warner Lake, OR

```{r,  warning=FALSE}
lakeWarner_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Warner Lake,OR'))
lakeWarner_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Warner Lake,OR'))
lakeWarner_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Warner Lake,OR'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeWarner_map + theme(legend.position = 'bottom'), lakeWarner_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map19 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeWarner_inset, x= 0.263, y = 0.105, width = 0.15, height = 0.15)

gg_inset_map19
```

#  Warner Lake, OR- Federal Lands
```{r}
lakeWarner_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Warner Lake,OR'))
lakeWarner_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Warner Lake,OR'))

combineFed <- plot_grid(lakeWarner_mapFed+ theme(legend.position = 'none'), lakeWarner_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map19Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeWarner_inset, x= 0.263, y = 0.052, width = 0.15, height = 0.15)

gg_inset_map19Fed 
```

# Winnemucca Lake, NV

```{r,  warning=FALSE}
lakeWinnemucca_map <- map_lake(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Winnemucca Lake,NV'))
lakeWinnemucca_chart <- chart_lakeLand(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Winnemucca Lake,NV'))
lakeWinnemucca_inset <- map_lake_inset(data_gbd=p1_gbd_bnd, data_lakes= p1_saline_lakes_sf, 
                                   data_watershed = p1_watershed_ext_sf, focal_lakes = c('Winnemucca Lake,NV'), proj = st_crs(p1_gbd_bnd))

combine <- plot_grid(lakeWinnemucca_map + theme(legend.position = 'bottom'), lakeWinnemucca_chart,rel_widths = c(0.60, 0.60), rel_heights = c(0.55, 0.55))

gg_inset_map20 = ggdraw() +
  draw_plot(combine) +
  draw_plot(lakeWinnemucca_inset, x= 0.120, y = 0.099, width = 0.125, height = 0.125)

gg_inset_map20
```

# Winnemucca Lake, NV - Federal Lands
```{r}
lakeWinnemucca_mapFed <- map_lakeFederal(data = p2_watershedExt_ByMngNm_reduce, join = p2_gbd_pal, zoom = 9, focal_lakes = c('Winnemucca Lake,NV'))
lakeWinnemucca_chartFed <- chart_lakeLandFed(data = p2_watershedExtByMngNm_grp_pArea, focal_lakes = c('Winnemucca Lake,NV'))

combineFed <- plot_grid(lakeWinnemucca_mapFed + theme(legend.position = 'none'), lakeWinnemucca_chartFed,rel_widths = c(0.60, 0.65), rel_heights = c(0.55, 0.55))

gg_inset_map20Fed = ggdraw() +
  draw_plot(combineFed) +
  draw_plot(lakeWinnemucca_inset,x= 0.095, y = 0.046, width = 0.15, height = 0.15)

gg_inset_map20Fed 
```
