---
title: "Land Ownership"
output: html_document
date: "2022-10-11"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load_lbs, echo = FALSE, message = FALSE, warnings = FALSE}
library(tidyverse)
library(here)
library(leaflet)
library(scico)
library(scales)
library(sf)
library(ggmap)
library(ggspatial)
library(rnaturalearthdata)
library(rnaturalearth)
library(ggsn)
library(rmapshaper)
library(maptiles)
library(tidyterra)
```

# Read in all shapefiles
```{r}
proj <- '+proj=aea +lat_0=35 +lon_0=-117 +lat_1=37.3 +lat_2=39.7 +x_0=0 +y_0=0 +ellps=GRS80 +towgs84=0,0,0,0,0,0,0 +units=m +no_defs'

# Read in watershed extents
watershed_ext <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/Saline_lake_watershed_extents/lake_watersheds.shp')) %>% 
  st_transform(crs=proj)

# saline lake 
saline_lakes <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/saline_lakes/saline_lakes.shp')) %>% 
  st_transform(crs=proj)

# Great Basin Dessert Band
gbd_bnd <- st_read(here('1_fetch/in/Vizlab-saline_lakes_spatial_data/GreatBasinDessertBnd_220721/GreatBasinDessertBnd.shp')) %>% 
  st_transform(crs=proj) |>
  ms_simplify()

#PAD/land ownership 
pad <- st_read(here('1_fetch/in/Shapefiles_220721/PADUS_3_0VA.shp')) %>% 
  st_transform(crs=proj) %>% 
  select(OBJECTI, Mng_Typ, Mang_Nm, Unit_Nm, GIS_Acr, MngTp_D, MngNm_D, MngNm_L, BndryNm, ST_Name) |>
  mutate(Mng_Level = case_when(
    Mng_Typ == 'FED' ~ 'Federal',
    Mng_Typ %in% c('LOC', 'STAT', 'DIST', 'JNT') ~ 'Regional/State/Local',
    Mng_Typ %in% c('PVT','UNK') ~ 'Private or Unknown',
    Mng_Typ == 'NGO' ~ 'NGO',
    Mng_Typ == 'TRIB' ~ 'Tribal Land'
  ))

# states
states <- st_read(here('1_fetch/in/states_shp/statesp010g.shp')) %>% 
  st_transform(crs=proj) |>
  ms_simplify()
```

# Intersect `pad` to each of `gbd_bnd, `saline_lakes`, and `watershed_ext`
```{r}

# add in an area count column to the dfs
gbd_pad_int <- gbd_bnd |> 
  st_intersection(pad) |>
  mutate(area = st_area(geometry))

saline_lakes_pad_int <- saline_lakes |> 
  st_intersection(pad) |>
  mutate(area = st_area(geometry))

watershed_ext_pad_int <- watershed_ext |> 
  st_intersection(pad) |>
  mutate(area = st_area(geometry))
```

# group data by Mng_Typ and calculate the total land area per Mng_Typ
```{r}
gbdByMng <- gbd_pad_int |>
  group_by(Mng_Typ) |>
  summarise(areaMng_Typ = as.numeric(sum(area))) |>
  arrange(desc(areaMng_Typ)) |>
  ms_simplify()

watershedExtByMng <- watershed_ext_pad_int %>%
  group_by(Mng_Typ, lk_w_st) %>%
  summarise(areaMng_Typ = as.numeric(sum(area)))|>
  ms_simplify()

```

# group data by MngNm_D and calculate the total land area per MngNm_D (more detailed Manamgement Types)
```{r}
## creating a grouping variable to assign color scales within (fewer colors)
gbdByMngNm <- gbd_pad_int |>
  group_by(Mng_Level, MngNm_D) |>
  summarise(areaMngNm_Typ = as.numeric(sum(area))) |>
  ms_simplify()
str(gbdByMngNm)

## what are thet top?
gbdByMngNm |> arrange(desc(areaMngNm_Typ))

watershedExtByMngNm <- watershed_ext_pad_int |>
  group_by(Mng_Level, MngNm_D, lk_w_st) |>
  summarise(areaMngNm_Typ = as.numeric(sum(area))) |>
  ms_simplify()

```


# Plot 
```{r}
ggplot(data = gbdByMngNm ) +
  geom_sf(aes(fill = Mng_Level))

ggplot(data = watershedExtByMngNm) +
  geom_sf(aes(fill = MngNm_D))

```

# Group some of the Management Type names to reduce colors needed 
```{r}
gbdByMngNm <- gbdByMngNm %>% 
  mutate(MngGroup = case_when(
   MngNm_D == "American Indian Lands" ~ "Native American areas", 
   MngNm_D == "Agricultural Research Service" ~ "Federal - other",
    MngNm_D == "Army Corps of Engineers" ~ "Federal - other", 
    MngNm_D == "Department of Energy" ~ "Federal - other",
    MngNm_D == "Natural Resources Conservation Service" ~ "Federal - other", 
    MngNm_D == "State Department of Conservation" ~ "State entities",
    MngNm_D == "Other or Unknown State Land" ~ "State entities", 
    MngNm_D == "State Park and Recreation" ~ "State entities",
    MngNm_D == "State Department of Land" ~ "State entities",
    MngNm_D == "State Fish and Wildlife" ~ "State entities", 
    MngNm_D == "State Department of Natural Resources" ~ "State entities", 
    MngNm_D == "State Land Board" ~ "State entities", 
    MngNm_D == "Regional Agency Land" ~ "Regional entites",
    MngNm_D == "County Land" ~ "Municipal entities",
    MngNm_D == "City Land" ~ "Municipal entities", 
    MngNm_D == "Non-Governmental Organization" ~ "NGO",
    TRUE ~ MngNm_D
  ))

watershedExtByMngNm <- watershedExtByMngNm %>% 
  mutate(MngGroup = case_when(
   MngNm_D == "American Indian Lands" ~ "Native American areas", 
   MngNm_D == "Agricultural Research Service" ~ "Federal - other",
    MngNm_D == "Army Corps of Engineers" ~ "Federal - other", 
    MngNm_D == "Department of Energy" ~ "Federal - other",
    MngNm_D == "Natural Resources Conservation Service" ~ "Federal - other", 
    MngNm_D == "State Department of Conservation" ~ "State entities",
    MngNm_D == "Other or Unknown State Land" ~ "State entities", 
    MngNm_D == "State Park and Recreation" ~ "State entities",
    MngNm_D == "State Department of Land" ~ "State entities",
    MngNm_D == "State Fish and Wildlife" ~ "State entities", 
    MngNm_D == "State Department of Natural Resources" ~ "State entities", 
    MngNm_D == "State Land Board" ~ "State entities", 
    MngNm_D == "Regional Agency Land" ~ "Regional entites",
    MngNm_D == "County Land" ~ "Municipal entities",
    MngNm_D == "City Land" ~ "Municipal entities", 
    MngNm_D == "Non-Governmental Organization" ~ "NGO",
    TRUE ~ MngNm_D
  ))

library(colorspace)
yellbr<- c('E6B325', 'A47E3B', 'YlOrRd', '', '', '', '')
sequential_hcl(7, palette = 'YlOrRd')
pal_mng <- gbdByMngNm |>
  st_drop_geometry() |>
  distinct(Mng_Level, MngGroup, MngNm_D) |>
  arrange(Mng_Level, MngGroup) |>
  mutate(color = c(sequential_hcl(7, palette = 'YlOrBr')[3:1], 
                   rep(sequential_hcl(7, palette = 'YlOrBr')[4], 4),
                   sequential_hcl(7, palette = 'YlOrBr')[5:7],
                   'dodgerblue',
                   'grey','grey',
                   sequential_hcl(12, palette = 'Purp')[1],
                   rep(sequential_hcl(12, palette = 'Purp')[2],2),
                   sequential_hcl(12, palette = 'Purp')[3:4],
                   sequential_hcl(12, palette = 'Purp')[5:11],
                   "pink"
                   
                   ))

```

```{r}

basemap <- get_tiles(x = gbdByMngNm, provider = "CartoDB.PositronNoLabels", crop = T, verbose = T, zoom = 7, forceDownload = T)

manualcolors<-c('black','forestgreen', 'red2', 'orange', 'cornflowerblue', 'darkolivegreen4', 'indianred1', 'tan4', 'darkblue','firebrick4',  'yellowgreen', 'lightsalmon', 'tan3','darkgray', 'wheat4', 'moccasin', 'mediumvioletred','cadetblue1',
                "darkolivegreen1" , "tomato3" , "#7CE3D8", "darkturquoise", "gainsboro")

newcolors<-c('#e5a415','#e8d274', 
             '#e58a63', '#f4f440', 
             'cornflowerblue', 'darkolivegreen4', 
             'indianred1', 'tan4', 
             'lavender','orangered',  
             'yellowgreen', 'lightsalmon', 
             'purple','darkgray', 
             'grey', 'moccasin', 
             'mediumvioletred','purple',
              "darkolivegreen1","tomato3" , 
             "#7CE3D8", "darkturquoise", 
             "gainsboro")

gbd_pal <- gbdByMngNm |>
  st_drop_geometry() |>
  group_by(Mng_Level) |>
  arrange(Mng_Level, MngGroup) |>
  mutate(ord = row_number()) 

greatBasin <- gbdByMngNm |>
  left_join(gbd_pal) |>
  ggplot() +
  geom_spatraster_rgb(data = basemap) +
  geom_sf(
          aes(fill = MngGroup), 
          color = NA,
          inherit.aes = FALSE) +
  coord_sf() +
  #scale_color_manual(values = manualcolors) +
  #scale_fill_manual(values = newcolors) + 
  scale_fill_scico_d(palette = 'batlow', direction = -1, end = 0.8) +
  labs(fill='') +
  scale_alpha(range = c(0.5, 1)) +
  guides() + 
  theme_void() +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        plot.background = element_rect(fill = 'white', color = NA)) +
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.2, "in"), pad_y = unit(0.15, "in"),
                         height = unit(0.35, "in"), width= unit(0.2, "in"),
                         style = north_arrow_orienteering(fill = c("black", "black"),
                                                          line_col = "black",
                                                          text_col = "black"))
greatBasin

ggsave(here("6_visualize/out/greatBasin.svg"), width = 10, height = 7, dpi = 300)

```

```{r}
mapBound <- watershedExtByMngNm %>% st_transform(crs=proj) %>% 
  st_bbox() %>% st_as_sfc() %>% st_buffer(0.25) %>%
  st_bbox() %>% as.numeric()

pyramid <- watershedExtByMngNm |>
  filter(lk_w_st %in% c('Pyramid Lake,NV', 'Winnemucca Lake,NV'))

basemap_pyramid <- get_tiles(x = pyramid, provider = "CartoDB.PositronNoLabels", crop = T, verbose = T, zoom = 9, forceDownload = T)

pyramid |>
  left_join(gbd_pal) |>
  ggplot() +
  geom_spatraster_rgb(data = basemap_pyramid |> terra::crop(pyramid)) +
  geom_sf(
          aes(fill = MngGroup), 
          color = NA, size = 0.2) + 
  #geom_sf(data = saline_lakes |> filter(lk_w_st %in% c('Pyramid Lake,NV', 'Winnemucca Lake,NV')), 
   #       fill = '#b2d8d8') +
  coord_sf() + 
  #scale_fill_manual(values = newcolors) + 
  scale_fill_scico_d(palette = 'batlow', direction = -1, end = 0.8) +
  labs(fill='Management Type') +
  guides(color="none") +
  theme_void() +
  scale_alpha(range = c(0.5, 1)) +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.key = element_blank()) +
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.2, "in"), pad_y = unit(0.15, "in"),
                         height = unit(0.35, "in"), width= unit(0.2, "in"),
                         style = north_arrow_orienteering(fill = c("black", "black"),
                                                          line_col = "black",
                                                          text_col = "black"))


ggsave(here("6_visualize/out/land_pyramidLake.svg"), width = 10, height = 7, dpi = 300)

```


```{r}

mono <- watershedExtByMngNm |>
  filter(lk_w_st %in% c('Mono Lake,CA'))

basemap_mono <- get_tiles(x = mono, provider = "CartoDB.PositronNoLabels", crop = T, verbose = T, zoom = 9, forceDownload = T)

mono |>
  left_join(gbd_pal) |>
  ggplot() +
  geom_spatraster_rgb(data = basemap_mono |> terra::crop(mono)) +
  geom_sf(
          aes(fill = MngGroup), 
          color = 'black',
          size = 0.2) + 
  geom_sf(data = saline_lakes |> filter(lk_w_st %in% c('Mono Lake,CA')), 
          fill = NA, color = 'white') +
  coord_sf() + 
  scale_fill_scico_d(palette = 'bamako', direction = -1, end = 0.8) +
  #scale_fill_manual(values = newcolors) + 
  scale_fill_scico_d(palette = 'batlow', direction = -1, end = 0.8) +
  labs(fill='Management Type') +
  guides(color="none") +
  theme_void() +
  theme(legend.position="bottom",
        legend.title=element_blank(),
        legend.key = element_blank()) +
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.2, "in"), pad_y = unit(0.15, "in"),
                         height = unit(0.35, "in"), width= unit(0.2, "in"),
                         style = north_arrow_orienteering(fill = c("black", "black"),
                                                          line_col = "black",
                                                          text_col = "black"))


ggsave(here("6_visualize/out/land_monoLake.svg"), width = 10, height = 7, dpi = 300)
```

# Percent of land charts
```{r}
# Great Basin level
gbdByMngNm_grp_pArea <- gbdByMngNm |> 
  st_drop_geometry() |>
  group_by(MngGroup) %>% 
  summarize(areaMngNm_Typ = sum(areaMngNm_Typ)) |>
  mutate(GB_area = sum(areaMngNm_Typ),
         Proportion = as.numeric(100 * (areaMngNm_Typ /GB_area)),
         Label = sprintf(" %s%%", round(Proportion, 1))) |>
  arrange(Proportion) |> 
  left_join(gbdByMngNm)

ggplot(data = gbdByMngNm_grp_pArea, 
       aes(y= Proportion, x=reorder(MngGroup, Proportion, FUN = sum))) +
  geom_bar(stat = "identity", 
           aes(fill = MngGroup)) +
  geom_text(aes(label = Label), 
            position = position_dodge(width = 0.9), # What is going on with some of these
            hjust= -0.01,
            size = 3.5) +
  geom_rect(ymin = -3, ymax = -1, xmin = seq(0.545, 15.545), xmax = seq(1.455, 16.455),
              aes(fill = Mng_Level)) +
  coord_flip() +
  #scale_fill_manual(values = newcolors) + 
  scale_fill_scico_d(palette = 'batlow', direction = -1, end = 0.8) +
  scale_y_continuous(breaks = seq(0, 70, by = 10), limits = c(NA, 60), position  = 'right') +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.minor.x = element_blank(),
        text = element_text(size=14)) +
  labs(y = "Percent of land within Great Basin", x = NULL) 

ggsave(here("6_visualize/out/chart_greatBasinLand.svg"), width = 7, height = 7, dpi = 300)
```


```{r}

# watershed lake level - Pyramid Lake, NV and Mono Lake, CA 
watershedExtByMngNm_lakeArea <- watershedExtByMngNm |>
  st_drop_geometry() |>
  group_by(lk_w_st) |> 
  summarise(areaMngNm_Typ = sum(areaMngNm_Typ)) 

watershedExtByMngNm_sum <-watershedExtByMngNm %>%  group_by(MngNm_D, lk_w_st) |> 
  summarize(area =sum(areaMngNm_Typ))

watershedExtByMngNm_pArea <- merge(x = watershedExtByMngNm_lakeArea, y = watershedExtByMngNm, by = "lk_w_st") |>
    filter(lk_w_st %in% c("Pyramid Lake,NV", 'Winnemucca Lake,NV')) |>  # filtering for Just Pyramid Lake and Mono Lake 
  group_by(Mng_Level, MngGroup, MngNm_D) |>
  summarize(areaMngNm_Typ.y = sum(areaMngNm_Typ.y),
            areaMngNm_Typ.x = sum(areaMngNm_Typ.x)) |>
  mutate(Proportion = as.numeric(100 * (areaMngNm_Typ.y /areaMngNm_Typ.x)),
         Label = sprintf(" %s%%", round(Proportion, 1))) |>
  arrange(-Proportion) 


ggplot(data = watershedExtByMngNm_pArea, 
       aes(y= Proportion, x=reorder(MngNm_D, Proportion))) +
  geom_bar(stat = "identity", 
           aes(fill=MngGroup)) +
  geom_text(aes(label = Label), 
            position = position_stack(vjust = 1), # What is going on with some of these
            hjust=-0.01,
            size = 3) +
  scale_y_continuous(breaks = seq(0, 40, by = 10), 
                     limits = c(NA, 35), 
                     position  = 'right') + 
  #scale_fill_manual(values = manualcolors) +
  scale_fill_scico_d(palette = 'batlow', direction = -1, end = 0.8) +
  geom_rect(data = watershedExtByMngNm_pArea |> distinct(Mng_Level, MngNm_D, Proportion), 
            aes(x=reorder(MngNm_D, Proportion,fill = MngGroup),
            ymin = -3, ymax = -1, 
            xmin = seq(0.545, 18.545), xmax = seq(1.455, 19.455))) + 
  coord_flip() +
  theme_minimal() +
  labs(y= "Percent of land within lake watershed",x=NULL) +
  theme(legend.position = "none",
        panel.grid.minor.x = element_blank())


ggsave(here("6_visualize/out/chart_lakeLand_pyramid.svg"), width = 7, height = 7, dpi = 300)

watershedExtByMngNm_pArea <- merge(x = watershedExtByMngNm_lakeArea, y = watershedExtByMngNm, by = "lk_w_st") |>
    filter(lk_w_st %in% c("Mono Lake,CA")) |>  # filtering for Just Pyramid Lake and Mono Lake 
  group_by(Mng_Level, MngGroup, MngNm_D) |>
  summarize(areaMngNm_Typ.y = sum(areaMngNm_Typ.y),
            areaMngNm_Typ.x = sum(areaMngNm_Typ.x)) |>
  mutate(Proportion = as.numeric(100 * (areaMngNm_Typ.y /areaMngNm_Typ.x)),
         Label = sprintf(" %s%%", round(Proportion, 1))) |>
  arrange(-Proportion) 


ggplot(data = watershedExtByMngNm_pArea, 
       aes(y= Proportion, x=reorder(MngNm_D, Proportion))) +
  geom_bar(stat = "identity", 
           aes(fill=MngGroup)) +
  geom_text(aes(label = Label), 
            position = position_stack(vjust = 1), # What is going on with some of these
            hjust=-0.01,
            size = 3) +
  scale_y_continuous(breaks = seq(0, 60, by = 10), 
                     limits = c(NA, 65), 
                     position  = 'right') + 
  #scale_fill_manual(values = manualcolors) +
  scale_fill_scico_d(palette = 'batlow', direction = -1, end = 0.8) +
  geom_rect(data = watershedExtByMngNm_pArea |> distinct(Mng_Level, MngNm_D, Proportion), 
            aes(x=reorder(MngNm_D, Proportion,fill = MngGroup),
            ymin = -3, ymax = -1, 
            xmin = seq(0.545, 9.545), xmax = seq(1.455, 10.455))) + 
  coord_flip() +
  theme_minimal() +
  labs(y= "Percent of land within lake watershed",x=NULL) +
  theme(legend.position = "none",
        panel.grid.minor.x = element_blank())


ggsave(here("6_visualize/out/chart_lakeLand_mono.svg"), width = 7, height = 7, dpi = 300)

```

# Percent of land charts
```{r}
# Great Basin level
gbdByMngNm_grp_pArea <- gbdByMngNm_grp %>% 
  st_drop_geometry() %>% 
  group_by(MngGroup) %>% 
  summarize(areaMngNm_Typ = sum(areaMngNm_Typ)) %>% 
  mutate(GB_area = sum(areaMngNm_Typ),
         Proportion = as.numeric(100 * (areaMngNm_Typ /GB_area)),
         Label = sprintf(" %s%%", round(Proportion, 0))) %>%
  arrange(Proportion)

ggplot(data = gbdByMngNm_grp_pArea, aes(y= Proportion, x=reorder(MngGroup, Proportion, FUN = sum))) +
  geom_bar(stat = "identity", 
           aes(fill=MngGroup)) +
    geom_text(aes(label = Label), position = position_dodge(width = 0.9), # What is going on with some of these
              hjust= -0.01,
              size = 3.5) +
geom_rect(ymin = -4, ymax = -1, xmin = seq(0.545, 15.545), xmax = seq(1.455, 16.455),
              aes(fill = MngGroup)) +
  coord_flip() +
  scale_fill_manual(values = manualcolors) + 
    scale_y_continuous(breaks = seq(0, 70, by = 10)) +
  theme_minimal() +
  theme(legend.position = "none",
        panel.grid.minor.x = element_blank(),
        text = element_text(size=14)) +
  labs(y= "Percent of land within Great Basin",x=NULL) 

ggsave(here("6_visualize/out/greatBasinChart.png"), width = 10, height = 7, dpi = 500)


# watershed lake level - Pyramid Lake, NV and Mono Lake, CA 
watershedExt5070ByMngNm_lakeArea <- watershedExt5070ByMngNm %>% 
  st_drop_geometry() %>% 
  group_by(lk_w_st) %>% 
  summarise(areaMngNm_Typ = sum(areaMngNm_Typ)) 

watershedExt5070ByMngNm_sum <-watershedExt5070ByMngNm %>%  group_by(MngNm_D, lk_w_st) %>% 
  summarize(area =sum(areaMngNm_Typ))

watershedExt5070ByMngNm_pArea <- merge(x = watershedExt5070ByMngNm_lakeArea, y = watershedExt5070ByMngNm, by = "lk_w_st") %>%
  st_drop_geometry %>%  
 mutate(Proportion = as.numeric(100 * (areaMngNm_Typ.y /areaMngNm_Typ.x)),
         Label = sprintf(" %s%%", round(Proportion, 0))) %>%
  arrange(-Proportion) %>% 
  filter(lk_w_st %in% c("Pyramid Lake,NV", "Mono Lake,CA")) %>%  # filtering for Just Pyramid Lake and Mono Lake per Cee's instructions 
slice_max(n=12, Proportion) %>% # plot top Land ownerships
  mutate(MngOrd = tidytext::reorder_within(MngNm_D, Proportion, lk_w_st)) # ordered land management by proportion and lake

ggplot(data = watershedExt5070ByMngNm_pArea, aes(y= Proportion, x=reorder(MngOrd, Proportion, FUN = sum))) +
 geom_bar(stat = "identity", 
           aes(fill=MngOrd)) +
  geom_text(aes(label = Label), position = position_stack(vjust = 1), # What is going on with some of these
              hjust=-0.01,
              size = 3) +
  scale_y_continuous(breaks = seq(0, 60, by = 10)) + 
  scale_fill_manual(values = manualcolors) + 
    facet_wrap(~lk_w_st,nrow=2,scales = "free_y") + 
    scale_x_reordered() + 
geom_rect(ymin = -4, ymax = -1, xmin = seq(0.545, 11.545), xmax = seq(1.455, 12.455),
              aes(fill = MngOrd)) + 
  coord_flip() +
  theme_minimal() +
  labs(y= "Percent of land within lake watershed extent",x=NULL) +
  theme(legend.position = "none",
        panel.grid.minor.x = element_blank())


ggsave(here("6_visualize/out/watershedLakeLevelChart.png"), width = 10, height = 7, dpi = 500)

```




